\papertitle

### 2013-01-31 manuscript.tex
added Stirling citation to bib and intro

The non-linear dynamics of flapping-wing flight compound 
these constraints~\cite{cheng:tandrdamping}\cite{humbert:dipteran2}. Much 
past research on flapping-wing MAVs focuses on overcoming the difficulties 
of controlling and modeling flapping-wing vehicles in the face of this
non-linearity\cite{floreano:flying}. Common approaches to simplify these 
dynamic models include averaging over the wing-beat 
period~\cite{cheng:tandrdamping}\cite{Schenato:flightcontrol}, and using 
linear, low-dimensional models to predict flight 
behavior~\cite{Shigeoka:ornithopter}. These advances led to the development 
of high-performance platforms such as the sub-15 gram DelFly, described by 
deCroon et al.~\cite{delfly:design}.

@@

The literature on cooperative control of MAVs is similarly limited to larger
vehicles or analytical explorations. Hyams et al., Jung et al. and Nebot et al. all 
demonstrated cooperative visual servoing for heterogeneous UGVs~\cite{Hyams1999Cooperative}\cite{Jung1998Range}\cite{Nebot2003Agents}. 
Luo, et al. and Mehta, et al. analyze  UAV-UGV cooperation from a modeling perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. 
Rudol et al. demonstrated a similar cooperative visual servoing system with 
UGVs and MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of 
magnitude larger than the lightweight systems we target, and so were able 
to take advantage of high-performance processors and specialized cameras.

>>>>

The non-linear dynamics of flapping-wing flight compound 
these constraints~\cite{cheng:tandrdamping}\cite{humbert:dipteran2}. Much 
past research on flapping-wing MAVs focuses on overcoming the difficulties 
of controlling and modeling flapping-wing vehicles in the face of this
non-linearity~\cite{floreano:flying}. Common approaches to simplify these 
dynamic models include averaging over the wing-beat 
period~\cite{cheng:tandrdamping}\cite{Schenato:flightcontrol}, and using 
linear, low-dimensional models to predict flight 
behavior~\cite{Shigeoka:ornithopter}. These advances led to the development 
of high-performance platforms such as the sub-15 gram DelFly, described by 
deCroon et al.~\cite{delfly:design}.

@@

The literature on cooperative control of MAVs is similarly limited to larger
vehicles or analytical explorations. Hyams et al., Jung et al. and Nebot et
al. all demonstrated cooperative visual servoing for heterogeneous
UGVs~\cite{Hyams1999Cooperative}\cite{Jung1998Range}\cite{Nebot2003Agents}.
Luo, et al. and Mehta, et al. analyze UAV-UGV cooperation from a modeling
perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. Rudol et al.
demonstrated a similar cooperative visual servoing system with UGVs and
MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of magnitude
larger than the lightweight systems we target, and so were able to take
advantage of high-performance processors and specialized cameras. Stirling et
al. describe a method for guiding quadrotors, designated as explorers, though
a network of stationary quadrotors, designated as beacons, through an indoor
environment~\cite{SwarmStirling}. The beacons provide external sensing for
navigating the explorers through the environment, and the network can be
extended by using explorers as beacons in undiscovered areas. Their
implementation relies solely on local sensing, although our size range
requires that the actual environment sensing be external to the MAV.
